`make.traits`

### 2022-03-11 inst/gitbook/02_make.traits.Rmd
typos + minors
Update 02_make.traits.Rmd

```{r}
## A simple Ornstein-Uhlenbeck motion process
my.OU.process <- function(x0, edge.length = 1, var = 1, alpha = 1, ...) {
    ## Calculate the mean based on alpha
    mean <- x0 * exp(-alpha)
    ## Calculate the standard deviation based on alpha and the variance
    sd <- sqrt(var/(2 * alpha) * (1 - exp(-2 * alpha)))
    ## Draw a random number from a normal distribution
    ## using this mean and standard deviation
    ## and depending on branch (edge) length
    result <- rnorm(n = 1, mean = mean, sd = sd * branch.length)

>>>>

```{r}
## A simple Ornstein-Uhlenbeck motion process
my.OU.process <- function(x0, edge.length = 1, var = 1, alpha = 1, ...) {
    ## Calculate the mean based on alpha
    mean <- x0 * exp(-alpha)
    ## Calculate the standard deviation based on alpha and the variance
    sd <- sqrt(var/(2 * alpha) * (1 - exp(-2 * alpha)))
    ## Draw a random number from a normal distribution
    ## using this mean and standard deviation
    ## and depending on branch (edge) length
    result <- rnorm(n = 1, mean = mean, sd = sd * edge.length)
